---
title: "Methods for Research and Policy Evaluation"
toc: true
---

This website aims to support the class 'Methods for Research and Policy Evaluation', thaught in the school of Public Affairs of Sciences Po. 

The objective of this course is to introduce quantitative methods for causal
inference, relying on mathematical formalization and applying them to concrete research situations.
Students will learn how to handle data - assembling a dataset, cleaning it, and preparing it for
quantitative analysis. The methods covered will include a review of linear models (simple and
multiple regressions) and nonlinear models (probit, logit), before moving on to the core of the
course: causal inference, namely DiD, RDD, and IV (2SLS, 2SRI). Each session will be divided equally
between the presentation of methods and their mathematical formulation, and in-class exercises
designed to help students master the associated coding techniques. The final goal is to replicate a
scientific article that applies one or more of these methods, enabling students to develop technical
skills useful for research or for the quantitative evaluation of public policies. Another objective is to
cultivate critical thinking regarding the strengths and limitations of such research methods. It is
therefore particularly well suited for students who wish to develop their skills in computer science,
mathematics, and quantitative research methods.

```{r}
1 + 1
```

$$
\begin{equation}
\hat{\beta} = (X'X)^{-1}X'y
\end{equation}
$$
First example:

::: {.panel-tabset group="language"}
# R
```{r}
2 + 2
```
# Python
```{python}
2 + 2
```
:::

Second example:

::: {.panel-tabset group="language"}
# R
```{r}
1 + 2
```
# Python
```{python}
1 + 2
```
:::
